Cluster Analysis: Identifying Parkinson's Disease Subtypes

### 2015-06-26 writeup/parkinsons.tex
add apcluster size table
Use full \linewidth for graphics
...since there's no reason to use 0.8

\begin{figure}[ht]
  \centering
  \includegraphics[width=0.8\linewidth]{pca-eigenvalues.png}
  \caption{Scree test: eigenvalues by factor}
  \label{fig:pca-eigenvalues}
\end{figure}

@@

\begin{figure}[ht]
  \centering
  \includegraphics[width=0.8\linewidth]{kmeans-wss-error.png}
  \caption{Scree test: WSS error by cluster size}
  \label{fig:kmeans-wss-error}
\end{figure}

@@

\begin{figure}[ht]
  \centering
  \includegraphics[width=0.8\linewidth]{gap-statistic.png}
  \caption{Gap statistic by cluster size}
  \label{fig:gap-statistic}
\end{figure}

@@

\begin{figure}[ht]
  \centering
  \includegraphics[width=0.8\linewidth]{asw.png}
  \caption{Average silhouette width by cluster size}
  \label{fig:asw}
\end{figure}

@@

\begin{figure}[ht]
  \centering
  \includegraphics[width=0.8\linewidth]{kmeans-silhouette-2.pdf}
  \caption{$k$-means cluster silhouette plot, $k = 2$}
  \label{fig:kmeans-silhouette-2}
\end{figure}

\begin{figure}[ht]
  \centering
  \includegraphics[width=0.8\linewidth]{kmeans-silhouette-3.pdf}
  \caption{$k$-means cluster silhouette plot, $k = 3$}
  \label{fig:kmeans-silhouette-3}
\end{figure}

\begin{figure}[ht]
  \centering
  \includegraphics[width=0.8\linewidth]{kmeans-silhouette-4.pdf}
  \caption{$k$-means cluster silhouette plot, $k = 4$}
  \label{fig:kmeans-silhouette-4}
\end{figure}

@@

\begin{figure}[ht]
  \centering
  \includegraphics[width=0.8\linewidth]{dtree-kmeans-pruned-unscaled-2.pdf}
  \caption{Decision Tree from $k$-means clustering, 2 clusters}
  \label{fig:kmeans-dtree-2}
\end{figure}

\begin{figure}[ht]
  \centering
  \includegraphics[width=0.8\linewidth]{dtree-kmeans-pruned-unscaled-3.pdf}
  \caption{Decision Tree from $k$-means clustering, 3 clusters}
  \label{fig:kmeans-dtree-3}
\end{figure}

\begin{figure}[ht]
  \centering
  \includegraphics[width=0.8\linewidth]{dtree-kmeans-pruned-unscaled-4.pdf}
  \caption{Decision Tree from $k$-means clustering, 4 clusters}
  \label{fig:kmeans-dtree-4}
\end{figure}

@@

AP with input preferences minimized ($q = 0$) resulted in 8 clusters.
With the standard median input preferences ($q = 0.5$), algorithm failed to
converge with default parameters. Even setting damping factor to 0.98, maximum
iterations to 10000, and convergence iterations to 1000 failed to converge.
Might need to try a longer term work.

@@

\begin{figure}[ht]
  \centering
  \includegraphics[width=0.8\linewidth]{ap-silhouette.pdf}
  \caption{AP silhouette plot, $k = 8$}
  \label{fig:ap-silhouette}
\end{figure}

@@

@@

\begin{figure}[ht]
  \centering
  \includegraphics[width=0.8\linewidth]{ap-summaries.pdf}
  \caption{AP Boxplot Summaries}
  \label{fig:ap-summaries}
\end{figure}

@@

\begin{figure}[ht]
  \centering
  \includegraphics[width=0.8\linewidth]{biclust-16.pdf}
  \caption{Biclustering $N = 16$}
  \label{fig:biclust-16}
\end{figure}

\begin{figure}[ht]
  \centering
  \includegraphics[width=0.8\linewidth]{bubbleplot-16.pdf}
  \caption{Bubbleplot $N = 16$}
  \label{fig:bubbleplot-16}
\end{figure}

>>>>

\begin{figure}[ht]
  \centering
  \includegraphics[width=\linewidth]{pca-eigenvalues.png}
  \caption{Scree test: eigenvalues by factor}
  \label{fig:pca-eigenvalues}
\end{figure}

@@

\begin{figure}[ht]
  \centering
  \includegraphics[width=\linewidth]{kmeans-wss-error.png}
  \caption{Scree test: WSS error by cluster size}
  \label{fig:kmeans-wss-error}
\end{figure}

@@

\begin{figure}[ht]
  \centering
  \includegraphics[width=\linewidth]{gap-statistic.png}
  \caption{Gap statistic by cluster size}
  \label{fig:gap-statistic}
\end{figure}

@@

\begin{figure}[ht]
  \centering
  \includegraphics[width=\linewidth]{asw.png}
  \caption{Average silhouette width by cluster size}
  \label{fig:asw}
\end{figure}

@@

\begin{figure}[ht]
  \centering
  \includegraphics[width=\linewidth]{kmeans-silhouette-2.pdf}
  \caption{$k$-means cluster silhouette plot, $k = 2$}
  \label{fig:kmeans-silhouette-2}
\end{figure}

\begin{figure}[ht]
  \centering
  \includegraphics[width=\linewidth]{kmeans-silhouette-3.pdf}
  \caption{$k$-means cluster silhouette plot, $k = 3$}
  \label{fig:kmeans-silhouette-3}
\end{figure}

\begin{figure}[ht]
  \centering
  \includegraphics[width=\linewidth]{kmeans-silhouette-4.pdf}
  \caption{$k$-means cluster silhouette plot, $k = 4$}
  \label{fig:kmeans-silhouette-4}
\end{figure}

@@

\begin{figure}[ht]
  \centering
  \includegraphics[width=\linewidth]{dtree-kmeans-pruned-unscaled-2.pdf}
  \caption{Decision Tree from $k$-means clustering, 2 clusters}
  \label{fig:kmeans-dtree-2}
\end{figure}

\begin{figure}[ht]
  \centering
  \includegraphics[width=\linewidth]{dtree-kmeans-pruned-unscaled-3.pdf}
  \caption{Decision Tree from $k$-means clustering, 3 clusters}
  \label{fig:kmeans-dtree-3}
\end{figure}

\begin{figure}[ht]
  \centering
  \includegraphics[width=\linewidth]{dtree-kmeans-pruned-unscaled-4.pdf}
  \caption{Decision Tree from $k$-means clustering, 4 clusters}
  \label{fig:kmeans-dtree-4}
\end{figure}

@@

Package \texttt{apcluster} was used. Distance matrix was the negative euclidean
squared distance ($r = 2$).

AP with input preferences minimized ($q = 0$) resulted in 8 clusters.
With the standard median input preferences ($q = 0.5$), algorithm failed to
converge with default parameters. Even setting damping factor to 0.98, maximum
iterations to 10000, and convergence iterations to 1000 failed to converge.
Might need to try a longer run.

@@

\begin{figure}[ht]
  \centering
  \includegraphics[width=\linewidth]{ap-silhouette.pdf}
  \caption{AP silhouette plot, $k = 8$}
  \label{fig:ap-silhouette}
\end{figure}

@@

Cluster sizes are available in Table~\ref{tab:ap-cluster-sizes}

\begin{table}[ht]
  \centering
  \begin{tabular}{l|l}
  Cluster & Size \\
  \hline
  1 & 54 \\
  2 & 68 \\
  3 & 25 \\
  4 & 259 \\
  5 & 102 \\
  6 & 68 \\
  7 & 185 \\
  8 & 20 \\
  \end{tabular}
  \caption{AP Cluster Sizes}
  \label{tab:ap-cluster-sizes}
\end{table}

@@

\begin{figure}[ht]
  \centering
  \includegraphics[width=\linewidth]{ap-summaries.pdf}
  \caption{AP Boxplot Summaries}
  \label{fig:ap-summaries}
\end{figure}

@@

\begin{figure}[ht]
  \centering
  \includegraphics[width=\linewidth]{biclust-16.pdf}
  \caption{Biclustering $N = 16$}
  \label{fig:biclust-16}
\end{figure}

\begin{figure}[ht]
  \centering
  \includegraphics[width=\linewidth]{bubbleplot-16.pdf}
  \caption{Bubbleplot $N = 16$}
  \label{fig:bubbleplot-16}
\end{figure}
